Spike-and-Slab Generalized Additive Models and Fast Algorithms for High-Dimensional Data

### 2021-06-02 Manuscript/01-Intro.Rmd
* Update manuscript writing * Set up targets for sub files

In many area of modern biomedical research, dealing with high-dimensional data, also known as $p >> n$ problem, is common,  for example sequencing data analysis, electric health record data analysis. Many statistical models have been proposed for such problem, for example, penalized models and Bayesian hierarchical models. However, up to this point, most efforts of methodology development focus on modeling linear effect in high dimensional setting. It is still not clear what is the best practice on how to model non-linear effects in high-dimensional setting. Similar to expanding classic models to high-dimensional models, expanding the GAM framework for high-dimensional applications is not a trivial task. The difficulties mainly come in two-fold: grouping nature of the basis functions, and the balance between spline smoothness and variable sparsity. For GAM models, a smoothing function is consists of multiple basis functions. The basis functions of a variable is inherently related. The grouping structure should be properly taken care of for accurate estimation. Moreover, shrinkage is previously used solely for sparsity of the model in high dimensional regression models, or smoothness in GAMs. How to organically combine the two together remains as a troubling question.

For high-dimensional data analysis, a common Bayesian modeling approach is to impose a particular family of priors, the spike-and-slab (SS) priors on the coeffcient in a regression modelss. The term "spike-and-slab" was first coined in @Mitchell1988 describing the shape of the prior. It is a mixture distribution, comprised with a skinny spike density $f_{spike}(\cdot)$ for weak signals and a flat slab density $f_{slab}(\cdot)$ for large signals, mathematically
$$
 \beta_i|\gamma_i \sim (1-\gamma_i)f_{spike}(\beta_i) + \gamma_if_{slab}(\beta_i).
$$

The most distinct feature of the SS priors family is that it is conditioned on a latent binary variable $\gamma_i$ that indicates whether the covariate $x_i$ is included in the model. There are various spike-and-slab priors depending on the choice for the spike density $f_{spike}(\cdot)$ and the slab density $f_{slab}(\cdot)$, for example @George1993; @George1997; @Chipman1996 for grouped variables; @Brown1998 for multivariate outcomes; @Ishwaran2005; @Clyde2004 and reference therein. Here we introduce the most popular spike-and-slab prior introduced in @George1993, as  stochastic search variable selection (SSVS). Given a regression problem
$$
Y = \bs X\beta+\epsilon, 
$$
we can assume the prior distribution of the regression parameters $\beta$ depends on a vector of binary variables $\gamma=(\gamma_1, \dots \gamma_p)^\prime$ as follows: given $\gamma_i$, $\beta_i$ are independent distributed as a mixture priors
$$
\beta_i | \gamma_i \sim (1-\gamma_i)N(0, \sigma^2 v_0) + \gamma_iN(0,\sigma^2 v_1).
$$
The prior of $\gamma$ is traditionally assumed to be identically independent Bernoulli distribution. Even the conjugate normal prior of $\bs \beta$ provides analytic simplicity, there is no closed form solution for the posterior density of $\bs \gamma$. @George1993 described a Gibbs sampling algorithm to approximate the posterior distribution of $\bs \gamma$ for variable selection. The same authors later compared SSVS with other Bayesian variable selection approaches, providing some empirical suggestions on the advantages and disadvantages of various formulations and estimation algorithms. [@George1997] Among the various problem SSVS addresses, high-dimensionality is not one of them, due to the intensive computation needs of MCMC algorithms. @George1997 suggested MCMC algorithms works well for medium size of predictors (p=25), which is not feasible for high-dimensional data, where the number of predictors easily exceeds 100.

To alleviate the computation burden, many methodology development studies focus on the maximum a posteriori (MAP) estimate [@Tipping2004]. EM-based algorithms are prevalent used to speed the computation. @Rockova2014a proposed an EM-based algorithm for a spike-and-slab Gaussian mixture prior, EMVS. The coefficient $\beta_j$ independently follows a mixture normal distribution $N(0, \sigma^2((1-\gamma_i)v_0 + \gamma_i v_1)$ for $0 \leq v_0 < v_1$. The parameter $\sigma^2$ follows a inverse gamma prior, $IG(v/2, v\lambda /2)$. Like in the spike-and slab family, the latent binary variables $\bs \gamma$ follows a Bernoulli prior with a hyper prior $\theta$ follows a beta distribution, or simpler the uniform (0,1). In the E step, the latent variable are treated as the missing data, and calculate the posterior mean of $\gamma$; in the M step, a ridge estimator was used to update the coefficients, and $\sigma^2, \theta$ are updated accordingly. As the ridge regression creates small but nonzero coefficients, a further step is needed to select the variable: EMVS further suggests to threshold the inclusion probability for variable selection or generate regularization plot with different values of the spike scale parameter. EMVS is also compatible with structured prior when dealing with grouped variables. The group structure can be imposed on the prior of the latent binary variable $\gamma$ via either logistic regression or markov random field.

The same authors [@Rockova2018b; @Rockova2018] further extended the continuous spike-and-slab Gaussian prior to the spike-and-slab double exponential distribution, as known as spike-and-slab lasso (SSL). The authors also lay the theoretical discussion of comparing spike-and-slab from the penalty perspective and the Bayesian perspective. The SSL also mitigated the problem of EMVS that the weak signals are not shrink to zero. Yi and his group incorporated the SSL prior in the EM-IWLS algorithm and proposed another EM algorithm, EM-cyclic coordinate descent, based on the Lasso penalty SSL exhibit. Such application were used in generalized linear models[@Tang2017a], cox models [@Tang2017] and their grouped counterparts[@Tang2018; @Tang2019]. Both EM based algorithm provide deterministic solutions, which becomes a more popular property as reproducible research becomes more valued. However, while the EMVS are not able to provide inference of the coefficients easily, the EM-IWLS can easily extract the variance-covariance matrix due to the IWLS algorithm. @Bai2020 provides an up-to-date summary of SSL methods and theoretical discussion.

To the best of our knowledge, there are few GAM models proposed for high dimensional application. In common practice, model matrix of spline terms are generated using base functions of preference, and then feed to a penalized model. Without proper handle of the grouping nature of bases functions, the estimation of the smooth function is less accurate. @Bai2020Spline shows inferior performance of such practice compared to using an ad hoc high-dimensional additive model.

Among the specialized high-dimensional spline methods, @Ravikumar2009 extended the original backfitting algorithm [@Hastie1987] to accommodate the high-dimensional setting. The sparsity and smoothness was handled separately with a soft threshold. The authors also demonstrated its similarity to Group Lasso. @Meier2009 proposed an a sparsity-smoothness penalty,

@@

In this article, we aim to address the challenges of non-linear signal modeling in high-dimensional application using Bayesian Hierarchical model. Specifically, we will propose a new Bayesian spike-and-slab prior for the generalized additive models and Cox spline models. The contribution of the proposed prior comes in two-fold: 1) it supports simultaneous variable selection and function selection; 2) it provides robust estimation and prediction for the coefficients and outcomes. As previously described, simultaneous variable selection and its functional form selection is not a trivial problem. Nevertheless, the Bayesian spike-and-slab prior is a perfect solution to the problem, as the latent binary indicator can be used to for variable selection and the spike and slab densities are used to adaptive adjust the smoothness of the spline function. Moreover, compared to currently available Bayesian spline models which mostly conduct a 'all-in-all-out' strategy, i.e. either including a non-linear form of a variable or excluding the variable completely, we offer a more flexible solution, rending one of three possibilities: no effect of a predictor, only linear effect of a predictor, or non-linear effect. This simplifies the process of determining what effect a predictor have on the outcome, without involving hypothesis testing where the degree of freedom for non-linear effect is complicated to estimate due to the shrinkage. Moreover, out model inherent the the robust estimation from Bayesian models.

Given the proposed model specification, the estimation of the parameters can be easily achieved with MCMC algorithm. Nevertheless, considering the computational burden MCMC algorithms bear especially in high-dimensional analysis, we propose parsimonious solutions, stemming from previous EM-IWLS [@Rockova2014a]and EM-coordinate descent algorithms[@Tang2018; @Tang2019]. The computational friendliness allows for fitting a model with different sets of initial values, mimicking the posterior sampling in the MCMC algorithms. We are hopeful that this could improve the sacrificed robustness of the estimation process due to the MAP estimation used by the EM algorithms in comparison to the model averaging approach.

The third aim of the dissertation work will focus on the software implementation of the proposed models and algorithms. We will implement the proposed models and algorithms in one of the most commonly used statistical computing environment R. Ancillary functions will be provided in assistance to model diagnostic, interpretation and graphing. The R implementation of the Bayesian Hierarchical additive model is available via a freely available R package, BHAM at (https://github.com/boyiguo1/BHAM)[https://github.com/boyiguo1/BHAM].

The rest of the paper are arranged as the followings: in Chapter 32 we demonstrate the Bayesian Hierarchical generalized additive model, where we provide the setup of the proposed model and two fast-fitting algorithms. In Chapter 3, we Application to real-world datasets demonstrates the usefulness of the proposed methodologies in Chpater 4. Conclusion and discussions are made in Chapter 5.

>>>>

In many area of modern biomedical research, dealing with high-dimensional data, also known as $p >> n$ problem, is common,  for example sequencing data analysis, electric health record data analysis. Many statistical models have been proposed for such problem, for example, penalized models and Bayesian hierarchical models. However, up to this point, most efforts of methodology development focus on modeling linear effect in high dimensional setting. It is still not clear what is the best practice on how to model non-linear effects in high-dimensional setting.

Similar to expanding classic models to high-dimensional models, expanding the GAM framework for high-dimensional applications is not a trivial task. The difficulties mainly come in two-fold: grouping nature of the basis functions, and the balance between spline smoothness and variable sparsity. For GAM models, a smoothing function is consists of multiple basis functions. The basis functions of a variable is inherently related. The grouping structure should be properly taken care of for accurate estimation. Moreover, shrinkage is previously used solely for sparsity of the model in high dimensional regression models, or smoothness in GAMs. How to organically combine the two together remains as a troubling question.

To the best of our knowledge, there are few GAM models proposed for high dimensional application. In common practice, model matrix of spline terms are generated using base functions of preference, and then feed to a penalized model. Without proper handle of the grouping nature of bases functions, the estimation of the smooth function is less accurate. @Bai2020Spline shows inferior performance of such practice compared to using an ad hoc high-dimensional additive model. Among the specialized high-dimensional spline methods, @Ravikumar2009 extended the original backfitting algorithm [@Hastie1987] to accommodate the high-dimensional setting. The sparsity and smoothness was handled separately with a soft threshold. The authors also demonstrated its similarity to Group Lasso. @Meier2009 proposed an a sparsity-smoothness penalty,

@@

In this article, we aim to address the challenges of non-linear signal modeling in high-dimensional application using Bayesian Hierarchical model. Specifically, we will propose a new Bayesian spike-and-slab prior for the generalized additive models and Cox spline models. The contribution of the proposed prior comes in two-fold: 1) it supports simultaneous variable selection and function selection; 2) it provides robust estimation and prediction for the coefficients and outcomes. As previously described, simultaneous variable selection and its functional form selection is not a trivial problem. Nevertheless, the Bayesian spike-and-slab prior is a perfect solution to the problem, as the latent binary indicator can be used to for variable selection and the spike and slab densities are used to adaptive adjust the smoothness of the spline function. Moreover, compared to currently available Bayesian spline models which mostly conduct a 'all-in-all-out' strategy, i.e. either including a non-linear form of a variable or excluding the variable completely, we offer a more flexible solution, rending one of three possibilities: no effect of a predictor, only linear effect of a predictor, or non-linear effect. This simplifies the process of determining what effect a predictor have on the outcome, without involving hypothesis testing where the degree of freedom for non-linear effect is complicated to estimate due to the shrinkage. Moreover, out model inherent the the robust estimation from Bayesian models. Lastly, The third aim of the dissertation work will focus on the software implementation of the proposed models and algorithms. We will implement the proposed models and algorithms in one of the most commonly used statistical computing environment R. Ancillary functions will be provided in assistance to model diagnostic, interpretation and graphing. The R implementation of the Bayesian hierarchical additive model is available via a freely available R package, BHAM at (https://github.com/boyiguo1/BHAM)[https://github.com/boyiguo1/BHAM].

The rest of the paper are arranged as the followings: in Chapter 2 we demonstrate the Bayesian Hierarchical generalized additive model, where we provide the setup of the proposed model and two fast-fitting algorithms. In Chapter 3, we Application to real-world datasets demonstrates the usefulness of the proposed methodologies in Chpater 4. Conclusion and discussions are made in Chapter 5.

### 2021-06-02 Manuscript/02-Method.Rmd
Add Flowchart to the table
* Update manuscript writing * Set up targets for sub files

@@

>>>>

## Spike and Slab Prior

For high-dimensional data analysis, a common Bayesian modeling approach is to impose a particular family of priors, the spike-and-slab (SS) priors on the coeffcient in a regression modelss. The term "spike-and-slab" was first coined in @Mitchell1988 describing the shape of the prior. It is a mixture distribution, comprised with a skinny spike density $f_{spike}(\cdot)$ for weak signals and a flat slab density $f_{slab}(\cdot)$ for large signals, mathematically
$$
 \beta_i|\gamma_i \sim (1-\gamma_i)f_{spike}(\beta_i) + \gamma_if_{slab}(\beta_i).
$$

The most distinct feature of the SS priors family is that it is conditioned on a latent binary variable $\gamma_i$ that indicates whether the covariate $x_i$ is included in the model. There are various spike-and-slab priors depending on the choice for the spike density $f_{spike}(\cdot)$ and the slab density $f_{slab}(\cdot)$, for example @George1993; @George1997; @Chipman1996 for grouped variables; @Brown1998 for multivariate outcomes; @Ishwaran2005; @Clyde2004 and reference therein. Here we introduce the most popular spike-and-slab prior introduced in @George1993, as  stochastic search variable selection (SSVS). Given a regression problem
$$
Y = \bs X\beta+\epsilon, 
$$
we can assume the prior distribution of the regression parameters $\beta$ depends on a vector of binary variables $\gamma=(\gamma_1, \dots \gamma_p)^\prime$ as follows: given $\gamma_i$, $\beta_i$ are independent distributed as a mixture priors
$$
\beta_i | \gamma_i \sim (1-\gamma_i)N(0, \sigma^2 v_0) + \gamma_iN(0,\sigma^2 v_1).
$$
The prior of $\gamma$ is traditionally assumed to be identically independent Bernoulli distribution. Even the conjugate normal prior of $\bs \beta$ provides analytic simplicity, there is no closed form solution for the posterior density of $\bs \gamma$. @George1993 described a Gibbs sampling algorithm to approximate the posterior distribution of $\bs \gamma$ for variable selection. The same authors later compared SSVS with other Bayesian variable selection approaches, providing some empirical suggestions on the advantages and disadvantages of various formulations and estimation algorithms. [@George1997] Among the various problem SSVS addresses, high-dimensionality is not one of them, due to the intensive computation needs of MCMC algorithms. @George1997 suggested MCMC algorithms works well for medium size of predictors (p=25), which is not feasible for high-dimensional data, where the number of predictors easily exceeds 100.

To alleviate the computation burden, many methodology development studies focus on the maximum a posteriori (MAP) estimate [@Tipping2004]. EM-based algorithms are prevalent used to speed the computation. @Rockova2014a proposed an EM-based algorithm for a spike-and-slab Gaussian mixture prior, EMVS. The coefficient $\beta_j$ independently follows a mixture normal distribution $N(0, \sigma^2((1-\gamma_i)v_0 + \gamma_i v_1)$ for $0 \leq v_0 < v_1$. The parameter $\sigma^2$ follows a inverse gamma prior, $IG(v/2, v\lambda /2)$. Like in the spike-and slab family, the latent binary variables $\bs \gamma$ follows a Bernoulli prior with a hyper prior $\theta$ follows a beta distribution, or simpler the uniform (0,1). In the E step, the latent variable are treated as the missing data, and calculate the posterior mean of $\gamma$; in the M step, a ridge estimator was used to update the coefficients, and $\sigma^2, \theta$ are updated accordingly. As the ridge regression creates small but nonzero coefficients, a further step is needed to select the variable: EMVS further suggests to threshold the inclusion probability for variable selection or generate regularization plot with different values of the spike scale parameter. EMVS is also compatible with structured prior when dealing with grouped variables. The group structure can be imposed on the prior of the latent binary variable $\gamma$ via either logistic regression or markov random field.

The same authors [@Rockova2018b; @Rockova2018] further extended the continuous spike-and-slab Gaussian prior to the spike-and-slab double exponential distribution, as known as spike-and-slab lasso (SSL). The authors also lay the theoretical discussion of comparing spike-and-slab from the penalty perspective and the Bayesian perspective. The SSL also mitigated the problem of EMVS that the weak signals are not shrink to zero. Yi and his group incorporated the SSL prior in the EM-IWLS algorithm and proposed another EM algorithm, EM-cyclic coordinate descent, based on the Lasso penalty SSL exhibit. Such application were used in generalized linear models[@Tang2017a], cox models [@Tang2017] and their grouped counterparts[@Tang2018; @Tang2019]. Both EM based algorithm provide deterministic solutions, which becomes a more popular property as reproducible research becomes more valued. However, while the EMVS are not able to provide inference of the coefficients easily, the EM-IWLS can easily extract the variance-covariance matrix due to the IWLS algorithm. @Bai2020 provides an up-to-date summary of SSL methods and theoretical discussion.

 Given the proposed model specification, the estimation of the parameters can be easily achieved with MCMC algorithm. Nevertheless, considering the computational burden MCMC algorithms bear especially in high-dimensional analysis, we propose parsimonious solutions, stemming from previous EM-IWLS [@Rockova2014a]and EM-coordinate descent algorithms[@Tang2018; @Tang2019]. The computational friendliness allows for fitting a model with different sets of initial values, mimicking the posterior sampling in the MCMC algorithms. We are hopeful that this could improve the sacrificed robustness of the estimation process due to the MAP estimation used by the EM algorithms in comparison to the model averaging approach.

@@

```{r}
include_graphics("Fig/SS_prior_flow_chart.png")
```

### 2021-06-02 Manuscript/SS_GAM.tex
* Update manuscript writing * Set up targets for sub files

In many area of modern biomedical research, dealing with
high-dimensional data, also known as \(p >> n\) problem, is common, for
example sequencing data analysis, electric health record data analysis.
Many statistical models have been proposed for such problem, for
example, penalized models and Bayesian hierarchical models. However, up
to this point, most efforts of methodology development focus on modeling
linear effect in high dimensional setting. It is still not clear what is
the best practice on how to model non-linear effects in high-dimensional
setting. Similar to expanding classic models to high-dimensional models,
expanding the GAM framework for high-dimensional applications is not a
trivial task. The difficulties mainly come in two-fold: grouping nature
of the basis functions, and the balance between spline smoothness and
variable sparsity. For GAM models, a smoothing function is consists of
multiple basis functions. The basis functions of a variable is
inherently related. The grouping structure should be properly taken care
of for accurate estimation. Moreover, shrinkage is previously used
solely for sparsity of the model in high dimensional regression models,
or smoothness in GAMs. How to organically combine the two together
remains as a troubling question.

@@

To the best of our knowledge, there are few GAM models proposed for high
dimensional application. In common practice, model matrix of spline
terms are generated using base functions of preference, and then feed to
a penalized model. Without proper handle of the grouping nature of bases
functions, the estimation of the smooth function is less accurate.
\citet{Bai2020Spline} shows inferior performance of such practice
compared to using an ad hoc high-dimensional additive model.

Among the specialized high-dimensional spline methods,
\citet{Ravikumar2009} extended the original backfitting algorithm
\citep{Hastie1987} to accommodate the high-dimensional setting. The
sparsity and smoothness was handled separately with a soft threshold.
The authors also demonstrated its similarity to Group Lasso.
\citet{Meier2009} proposed an a sparsity-smoothness penalty,

In this article, we aim to address the challenges of non-linear signal
modeling in high-dimensional application using Bayesian Hierarchical
model. Specifically, we will propose a new Bayesian spike-and-slab prior
for the generalized additive models and Cox spline models. The
contribution of the proposed prior comes in two-fold: 1) it supports
simultaneous variable selection and function selection; 2) it provides
robust estimation and prediction for the coefficients and outcomes. As
previously described, simultaneous variable selection and its functional
form selection is not a trivial problem. Nevertheless, the Bayesian
spike-and-slab prior is a perfect solution to the problem, as the latent
binary indicator can be used to for variable selection and the spike and
slab densities are used to adaptive adjust the smoothness of the spline
function. Moreover, compared to currently available Bayesian spline
models which mostly conduct a `all-in-all-out' strategy, i.e.~either
including a non-linear form of a variable or excluding the variable
completely, we offer a more flexible solution, rending one of three
possibilities: no effect of a predictor, only linear effect of a
predictor, or non-linear effect. This simplifies the process of
determining what effect a predictor have on the outcome, without
involving hypothesis testing where the degree of freedom for non-linear
effect is complicated to estimate due to the shrinkage. Moreover, out
model inherent the the robust estimation from Bayesian models.

@@

The third aim of the dissertation work will focus on the software
implementation of the proposed models and algorithms. We will implement
the proposed models and algorithms in one of the most commonly used
statistical computing environment R. Ancillary functions will be
provided in assistance to model diagnostic, interpretation and graphing.
The R implementation of the Bayesian Hierarchical additive model is
available via a freely available R package, BHAM at
(\url{https://github.com/boyiguo1/BHAM}){[}\url{https://github.com/boyiguo1/BHAM}{]}.

The rest of the paper are arranged as the followings: in Chapter 32 we
demonstrate the Bayesian Hierarchical generalized additive model, where
we provide the setup of the proposed model and two fast-fitting
algorithms. In Chapter 3, we Application to real-world datasets
demonstrates the usefulness of the proposed methodologies in Chpater 4.
Conclusion and discussions are made in Chapter 5.

@@

>>>>

In many area of modern biomedical research, dealing with
high-dimensional data, also known as \(p >> n\) problem, is common, for
example sequencing data analysis, electric health record data analysis.
Many statistical models have been proposed for such problem, for
example, penalized models and Bayesian hierarchical models. However, up
to this point, most efforts of methodology development focus on modeling
linear effect in high dimensional setting. It is still not clear what is
the best practice on how to model non-linear effects in high-dimensional
setting.

Similar to expanding classic models to high-dimensional models,
expanding the GAM framework for high-dimensional applications is not a
trivial task. The difficulties mainly come in two-fold: grouping nature
of the basis functions, and the balance between spline smoothness and
variable sparsity. For GAM models, a smoothing function is consists of
multiple basis functions. The basis functions of a variable is
inherently related. The grouping structure should be properly taken care
of for accurate estimation. Moreover, shrinkage is previously used
solely for sparsity of the model in high dimensional regression models,
or smoothness in GAMs. How to organically combine the two together
remains as a troubling question.

To the best of our knowledge, there are few GAM models proposed for high
dimensional application. In common practice, model matrix of spline
terms are generated using base functions of preference, and then feed to
a penalized model. Without proper handle of the grouping nature of bases
functions, the estimation of the smooth function is less accurate.
\citet{Bai2020Spline} shows inferior performance of such practice
compared to using an ad hoc high-dimensional additive model. Among the
specialized high-dimensional spline methods, \citet{Ravikumar2009}
extended the original backfitting algorithm \citep{Hastie1987} to
accommodate the high-dimensional setting. The sparsity and smoothness
was handled separately with a soft threshold. The authors also
demonstrated its similarity to Group Lasso. \citet{Meier2009} proposed
an a sparsity-smoothness penalty,

In this article, we aim to address the challenges of non-linear signal
modeling in high-dimensional application using Bayesian Hierarchical
model. Specifically, we will propose a new Bayesian spike-and-slab prior
for the generalized additive models and Cox spline models. The
contribution of the proposed prior comes in two-fold: 1) it supports
simultaneous variable selection and function selection; 2) it provides
robust estimation and prediction for the coefficients and outcomes. As
previously described, simultaneous variable selection and its functional
form selection is not a trivial problem. Nevertheless, the Bayesian
spike-and-slab prior is a perfect solution to the problem, as the latent
binary indicator can be used to for variable selection and the spike and
slab densities are used to adaptive adjust the smoothness of the spline
function. Moreover, compared to currently available Bayesian spline
models which mostly conduct a `all-in-all-out' strategy, i.e.~either
including a non-linear form of a variable or excluding the variable
completely, we offer a more flexible solution, rending one of three
possibilities: no effect of a predictor, only linear effect of a
predictor, or non-linear effect. This simplifies the process of
determining what effect a predictor have on the outcome, without
involving hypothesis testing where the degree of freedom for non-linear
effect is complicated to estimate due to the shrinkage. Moreover, out
model inherent the the robust estimation from Bayesian models. Lastly,
The third aim of the dissertation work will focus on the software
implementation of the proposed models and algorithms. We will implement
the proposed models and algorithms in one of the most commonly used
statistical computing environment R. Ancillary functions will be
provided in assistance to model diagnostic, interpretation and graphing.
The R implementation of the Bayesian hierarchical additive model is
available via a freely available R package, BHAM at
(\url{https://github.com/boyiguo1/BHAM}){[}\url{https://github.com/boyiguo1/BHAM}{]}.

The rest of the paper are arranged as the followings: in Chapter 2 we
demonstrate the Bayesian Hierarchical generalized additive model, where
we provide the setup of the proposed model and two fast-fitting
algorithms. In Chapter 3, we Application to real-world datasets
demonstrates the usefulness of the proposed methodologies in Chpater 4.
Conclusion and discussions are made in Chapter 5.

\hypertarget{spike-and-slab-prior}{%
\subsection{Spike and Slab Prior}\label{spike-and-slab-prior}}

@@

@@

@@

Remaining issue: 1. Degree of freedom has yet to closely studied. As an
direct impact, the functional selection can be improved when effective
degree of freedom are more carefully studied 2. Future exapansion, as we
were analyzing the metabolites data, we observed that metabolites
pathway infromation can be useful in the predictive and integrative
model can be developed based on the proposed framework. As an naive
solution, the selection indicator of linear effect of the spline terms
of all metabolites on the same pathway can be set to share the same
hyper prior such that the group selection can be modestly achieved.
Meanwhile further advancedment of the methodology regarding to the
integrative analysis can consider setting the hypor priors of the
selection indivator of the non-linear components conditioning on the
probability of inclusion of the linear effect. Such structure is more
sensible analytically.

### 2021-06-02 Manuscript/main.Rmd
Add Flowchart to the table
* Update manuscript writing * Set up targets for sub files

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r child="01-Intro.Rmd"}
```

```{r child="02-Method.Rmd"}
```

```{r child="03-Simulation.Rmd"}
```

```{r child="04-Real_Data.Rmd"}
```

```{r child="05-Discussion.Rmd"}
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(knitr)
library(targets)
library(here)

tar_load(intro_path)
tar_load(method_path)
tar_load(sim_path)
tar_load(real_data_path)
tar_load(disc_path)
```

```{r child=here(intro_path)}
```

```{r child=here(method_path)}
```

```{r child=here(sim_path)}
```

```{r child=here(real_data_path)}
```

```{r child=here(disc_path)}
```

### 2021-06-02 Manuscript/main.tex
* Update manuscript writing * Set up targets for sub files

\includegraphics[width=24.76in]{Fig/SS_prior_flow_chart}

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

>>>>

\includegraphics{Fig/SS_prior_flow_chart.png}

@@

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

Remaining issue: 1. Degree of freedom has yet to closely studied. As an
direct impact, the functional selection can be improved when effective
degree of freedom are more carefully studied 2. Future exapansion, as we
were analyzing the metabolites data, we observed that metabolites
pathway infromation can be useful in the predictive and integrative
model can be developed based on the proposed framework. As an naive
solution, the selection indicator of linear effect of the spline terms
of all metabolites on the same pathway can be set to share the same
hyper prior such that the group selection can be modestly achieved.
Meanwhile further advancedment of the methodology regarding to the
integrative analysis can consider setting the hypor priors of the
selection indivator of the non-linear components conditioning on the
probability of inclusion of the linear effect. Such structure is more
sensible analytically.
